---
title: "JonathanWilson-TidyTuesday1"
author: "JJWilson"
date: "01/10/2019"
output: html_document
---
```{r}
#Load packages needed for wrangling

library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(zipcode)
library(janitor)
data(zipcode)
```
```{r}
#Obtain data for tidy tuesday on pizza



pizza_jared <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_jared.csv")
pizza_barstool <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv")
pizza_datafiniti <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_datafiniti.csv")

```
```{r}
p1 <- pizza_barstool
p2 <- pizza_datafiniti
p3 <- pizza_jared
```
```{r}
glimpse(p1)

```
```{r}
glimpse(p2)
```
```{r}
glimpse(p3)
```
# Glimpsing at the data, the second set contains by far the most observations, but only price and location data, might be useful for plotting areas for more expensive pizza?
# Set 1 has the most in depth ratings it appears, whereas set 3 is categorical rating at good, excellent etc.
```{r}
# look at city data from p2




unique(p2$city)
```
# Way too many cities to deal with here
# Lets look at state, in this case labeled province to see if all are represented.
```{r}
unique(p2$province)
```
# 44 states represented which is quite good, but interesting that some aren't as I'm quite sure every state has pizza, maybe some states just don't have any worth eating?
# Lets see which states are most represented.
```{r}
numberperstate <- table(p2$province)

numberperstate

```
# Seeing as I'm new to GA, lets have a play with the GA data. maybe there is pizza worth eating in Athens?
## Although another interesting number is that New Jersey apparently only has 4 observations, possibly because people enter New york as the city observation when they're in the New york Metro area which then fills the state in as NY even if a large part of the Metro is in NJ?

```{r}
GApizza <- p2 %>% filter(province == "GA")

```
# GA is pretty well represented in the second data set with 214 observations, what about Athens?

```{r}
Athens <- GApizza %>% filter(city == "Athens")

```
# Oh... well we only have 2 observations for Athens so thats a bit of a dead end...
# Lets move on and plot the reviews from data set 1 on a map.
# We'll clean it up to remove any reviews without latitude and longitude values.

```{r}

p1clean = p1 %>%
  filter(!is.na(longitude)) 
usa <- map_data("usa") 
ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group = group), fill = NA, color = "black") +     coord_fixed(1.3) +  geom_point(data = p1clean, aes(x = longitude, y = latitude),   color = "blue", alpha = 0.25, size = 2)
usa
```
# From this quick map of the second data set we see the majority of observations are around NYC.  
# Lets rank the number of reviews per city.
```{r}
pizzacity = p1clean %>% 

  group_by(city) %>%

  summarize(num_per_city = n()) %>%

  arrange(desc(num_per_city))



pizzacity
```
# I wonder if there are any general trends in ratings relating to latitude and longitude...
```{r}
 p1clean %>% ggplot(aes(review_stats_all_average_score, longitude)) + geom_point() + geom_smooth(method = "lm")

```
```{r}
 p1clean %>% ggplot(aes(review_stats_all_average_score, latitude)) + geom_point() +geom_smooth(method = "lm")

```
# In both cases the data from NYC is overwhelming everything else, so lets remove the NYC data and see if anything emerges.
# Its becoming clear that the data roughly splits into 2 groups, New york and everywhere else, so I guess the options are to focus on one or the other or compare them.
```{r}
notny <- p1clean %>% filter(city != "New York")
notny %>% ggplot(aes(review_stats_all_average_score, latitude)) + geom_point() +geom_smooth(method = "lm")
```
```{r}
notny %>% ggplot(aes(review_stats_all_average_score, longitude)) + geom_point() +geom_smooth(method = "lm")
```
# There appears to be a reasonable trend between longitude and increased ratings now, suggesting locations on the east coast are generally getting higher ratings.
# Lets plot ratings of New York vs "Everybody Else".

```{r}
NYC1 = p1clean %>%

  filter(city == "New York")

NYC1
```
```{r}
vNYC1 <- NYC1 %>% ggplot(aes(x=city, y=review_stats_all_average_score)) + geom_violin() + geom_point()
vNYC1

```
```{r}
NYC1mean = p1clean %>%

  filter(city == "New York") %>%

  summarize(score = mean(review_stats_all_average_score))

NYC1mean
```
```{r}
NNYC1mean = p1clean %>%

  filter(city != "New York") %>%

  summarize(score = mean(review_stats_all_average_score))

NNYC1mean
```
# Just looking at the means, the non NYC has a higher mean rating.
# Lets create a new column with just a true or false for NYC...
```{r}
NYCCLEAN <- p1clean %>% mutate(NewYork = city == "New York")
glimpse(NYCCLEAN)
```
# Now lets plot our rating ditribution of NYC vs eveyone else with violin ploys and add our mean rating on there
```{r}
VSNYC1 <- NYCCLEAN %>% ggplot(aes(x=NewYork, y=review_stats_all_average_score)) + geom_violin() + geom_point() + stat_summary(fun.y=mean, geom="point", shape=23, size=3, color= "red", fill="red")
VSNYC1

```
# Looking at our two nice sting rays here it looks like not NYC is winning, but this could be due to NYC being heavily sampled across a whole range of pizza places but the reviewers may be more likely to sample somehwere with a reputation for good pizza outside of the Big Apple.